Online Verification of Commutativity

### 2020-08-11 acmPaper/paper.tex
Notation fixes

\section{Solving the online addition problem}

We present a polynomial time solution to the \textsc{verification set} problem.
Like with the baseline, we do not concern ourselves with parallel pairs where neither or both paths pass through the new edge.
The key observation that allows us to improve on the online baseline is that, for a given source and sink pair, only a single parallel pair needs to be verified. 
This is an implication of Theorem \ref{reductionRule}, expanded on later.
Theorem \ref{verifyingSet} shows that should our selected set of pairs along with cycles passing through the new edge be verified commutative, the entire diagram must commute. 
The approach is to identify a parallel pair with exactly one path through the edge for each (source, sink) pair (algorithm ~\ref{algo_online_polynomial}).

@@

The bound is asymptotically tight. This can be seen in the case where the graph contains 2N nodes besides S and T. We consider N of the nodes to be in group 1, and the other N to be in group 2. Every node in group 1 has a forward node to every node in group 2, as well as to S. T has a forward edge to every node in group 2. In this diagram, on the addition of edge (S, T), $N^2$ paths need to be verified which is polynomial in 2N+2.

Also notice that if trying to optimize for path length (say, if composing functions is expensive) then "find any path" can be replaced with "find shortest path".

>>>>

\section{Solving the Online Addition Problem}

We present a polynomial time solution to the \textsc{verification set} problem.
\xxx[as]{Elsewhere, ``problem'' is also in small-caps. Either way is fine, but consistency is important.}
Like in the online baseline algorithm, we do not concern ourselves with parallel pairs where neither or both paths pass through the new edge.
The key observation that allows us to improve on the online baseline is that, for a given source and sink pair, only a single parallel pair needs to be verified.
This is an implication of Theorem~\ref{reductionRule}, expanded on later.
Theorem~\ref{verifyingSet} shows that should our selected set of pairs along with cycles passing through the new edge be verified commutative, the entire diagram must commute.
The approach is to identify a parallel pair with exactly one path through the edge for each (source, sink) pair (\ref{algo_online_polynomial}).

@@

The bound is asymptotically tight. This can be seen in the case where the graph contains $2N$ nodes besides $S$ and $T$. We consider $N$ of the nodes to be in group 1, and the other $N$ to be in group 2. Every node in group 1 has a forward node to every node in group 2, as well as to $S$. $T$ has a forward edge to every node in group 2. In this diagram, on the addition of edge $(S, T)$, $N^2$ paths need to be verified which is polynomial in $2N+2$.

Also notice that if trying to optimize for path length (say, if composing functions is expensive) then ``find any path'' can be replaced with ``find the shortest path.''
